Timid tides or tall tails? \\ Investigating the outer reaches of the Sculptor and Ursa Minor dwarf galaxies

### 2025-04-25 thesis/appendix.tex
thesis updates and completed test fbest notebook

>>>>

\section{Appendix / Extra Notes}\label{appendix-extra-notes}

\subsection{Additional density profile
tests}\label{additional-density-profile-tests}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_density_methods_extra.pdf}}
\caption[Density profiles]{Density profiles for various assumptions for
Sculptor. PSAT is our fiducial 2-component J+24 sample, circ is a
2-component bayesian model assuming circular radii, simple is the series
of simple cuts described in Appendix ?, bright is the sample of the
brightest half of stars (scaled by 2), DELVE is a sample of RGB stars
(background subtracted and rescaled to
match).}\label{fig:sculptor_observed_profiles}
\end{figure}

Note that a full rigorous statistical analysis would require a
simulation study of injecting dwarfs into Gaia and assessing the
reliability of various methods of membership and density profiles. This
is beyond the scope of this thesis.

\begin{verbatim}
SELECT TOP 1000
       *
FROM delve_dr2.objects
WHERE 11 < ra
and ra < 19
and -37.7 < dec
and dec < -29.7
\end{verbatim}

\subsection{Velocity fit parameters.}\label{velocity-fit-parameters.}

Savage-Dickey calculated bayes factor using Silverman-bandwidth KDE
smoothed samples from posterior/prior.

\emph{Is it interesting that the velocity dispersion of Scl seems to
increase significantly with Rell?}

\begin{table*}[t]
\centering
\caption{MCMC fits for different RV datasets for Scl amoung 3 different models.}
\label{tbl:MCMC-fits-for-different-RV-datasets-for-Scl-amoung-3-different-models}
\begin{tabular}{lllllll}
\toprule
study & mean & sigma & $\partial \log\sigma / \partial \log R$ & $\partial v_z / \partial x$ (km/s/deg) & $\theta_{\rm grad} / ^{\circ}$ & $\log bf$\\
\midrule
all &  &  &  &  &  & \\
 & $111.18\pm0.23$ & $9.71\pm0.17$ & - & - & - & 0\\
 & $111.19 \pm 0.23$ & $9.68\pm0.17$ & - & $4.3\pm1.3$ & $-149_{-13}^{+17}$ & -1.7\\
 & $111.16\pm0.23$ & $9.73\pm0.17$ & $0.056\pm0.021$ & - & - & -0.9\\
tolstoy+23 &  &  &  &  &  & \\
 & $111.3 \pm 0.3$ & $9.80 \pm 0.18$ & - & - & - & 0\\
 & $111.3\pm0.3$ & $9.78\pm0.18$ & – & $4.3\pm1.4$ & $-154_{-13}^{+19}$ & -1.4\\
 & $111.2 \pm 0.3$ & $9.74\pm0.19$ & $0.085 \pm 0.023$ & – & – & -4.5\\
walker+09 &  &  &  &  &  & \\
 & $111.0\pm0.3$ & $9.57\pm0.21$ & – & – & – & 0\\
 & $111.1\pm0.3$ & $9.53\pm0.21$ & - & $5.2_{-1.6}^{+1.8}$ & $-134_{-16}^{+23}$ & -2.4\\
 & $111.0\pm0.3$ & $9.61\pm0.21$ & $0.03\pm0.03$ & – & – & +1.6\\
apogee &  &  &  &  &  & \\
 & $109.9\pm0.8$ & $8.3\pm0.6$ & – & – & – & –\\
 & $109.9\pm0.8$ & $8.3\pm0.6$ & – & $6\pm3$ & $-151_{-36}^{+44}$ & +0.4\\
 & $109.9\pm0.8$ & $8.3\pm0.7$ & $0.05\pm0.08$ & – & – & +1.1\\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption{MCMC fits for UMi velocity dispersion.}
\label{tbl:MCMC-fits-for-UMi-velocity-dispersion}
\begin{tabular}{lllll}
\toprule
study & mean & sigma & $\log bf_{\rm sigma}$ & $\log bf_{\rm grad}$\\
\midrule
all & $-245.9\pm0.3$ & $8.76\pm0.24$ & +1.5 & +2.2\\
pace & $-244.5\pm0.4$ & $9.1\pm0.3$ & +0.2 & +1.1\\
spencer & $-246.9\pm0.4$ & $8.8\pm0.3$ & +1.8 & -0.3\\
apogee & $-248.2\pm1.6$ & $9.0_{-1.1}^{+1.3}$ & +0.8 & +0.8\\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption{Summary of velocity measurements and derived properties. sestito+2023a number of members depends on spatial model used.}
\label{tbl:Summary-of-velocity-measurements-and-derived-properties-sestito+2023a-number-of-members-depends-on-spatial-model-used}
\begin{tabular}{llllllll}
\toprule
 & Study & Instrument & Nspec & Nstar & Ngood & Nmemb & $\delta v_{\rm med}$\\
\midrule
Scl & combined &  & 8945 & 2280 & 2034 & 1918 & 0.9\\
 & tolstoy+23 & FLAMES & 3311 & 1701 & 1522 & 1480 & 0.65\\
 & sestito+23a & GMOS & 2 & 2 & 2 & 2 & 13\\
 & walker+09 & MMFS & 1818 & 1522 & 1417 & 1329 & 1.8\\
 & APOGEE & APOGEE & 5082 & 253 & 102 & 98 & 0.6\\
UMi & combined &  & 4714 & 1225 & 1148 & 831 & 2.3\\
 & sestito+23b & GRACES & 5 & 5 & 5 & 5 & 1.8\\
 & pace+20 & DEIMOS & 1716 & 1538 & 829 & 682 & 2.5\\
 & spencer+18 & Hectoshell & 1407 & 970 & 596 & 406 & 0.9\\
 & APOGEE & APOGEE & 9500 & 279 & 37 & 32 & 0.9\\
\bottomrule
\end{tabular}
\end{table*}

\section{Numerical Convergence}\label{numerical-convergence}

### 2025-04-25 thesis/data.tex
thesis updates and completed test fbest notebook

\begin{itemize}
\tightlist
\item
  Solved parallax, proper motions, colour, and magnitudes.
\item
  High quality astrometry (\texttt{ruwe\ \textless{}=\ 1.3}).
\item
  3\(\sigma\) consistency of measured parallax with dwarf distance +
  uncertainty (typically near zero; with \citet{lindegren+2018}
  zero-point correction).
\item
  Absolute RA and Dec proper motions less than
  10\(\,{\rm mas\ yr^{-1}}\) (corresponding to tangental velocities of
  \(\gtrsim 500\) km/s at distances larger than 10 kpc.).
\item
  No colour excess (\citet{lindegren+2018} equation C.2).
\item
  22 \textgreater{} G \textgreater{} 5\(\sigma\) brighter than TRGB (in
  practice astrometry ruwe =\textgreater{} 21 \textgreater{} G).
\item
  Between -0.5 and 2.5 in Bp - Rp.
\end{itemize}

Photometry is dereddened using \citet{schlegel+1988} extinction maps.

@@

Finally, we need to correct the coordinate frames for the solar motion
and on-sky size of the galaxy. The first step is to subtract out the
solar motion from each radial velocity, corresponding to a typical
gradient of \textasciitilde3 km/s across the field. The next step is to
account for the slight differences in the direction of each radial
velocity. Define the \(\hat z\) direction to point parallel to the
direction from the sun to the centre of the dwarf galaxy. Then if
\(\phi\) is the angular distance between the centre of the galaxy and
the individual star, the corrected radial velocity is then \[
v_z = v_{\rm los, gsr}\cos\phi  - v_{\alpha}\cos\theta \sin\phi - v_\delta \sin\theta\sin\phi
\] where
\(v_{\rm tan, R} = d(\mu_{\alpha*}\cos\theta + \mu_\delta \sin \theta)\)
is the radial component of the proper motion with respect to the centre
of the galaxy.This correction is of the order \(v_{\rm tan}\theta\) so
induces a gradient of about \(1 km/s/degree\) for sculptor
\citep[see][]{WMO2008}. The uncertainty is then the velocity uncertainty
plus the distance uncertainties times the PM uncertainty from above. We
then use the \(v_z\) values for the following modelling, however
repeating with uncorrected, heliocentric velocities does not
significantly affect the results .

@@

\subsection{}\label{section}

\begin{table*}[t]
\centering
\caption{Summary of velocity measurements and derived properties. sestito+2023a number of members depends on spatial model used.}
\label{tbl:Summary-of-velocity-measurements-and-derived-properties-sestito+2023a-number-of-members-depends-on-spatial-model-used}
\begin{tabular}{llllllll}
\toprule
 & Study & Instrument & Nspec & Nstar & Ngood & Nmemb & $\delta v_{\rm med}$\\
\midrule
Scl & combined &  & 8945 & 2280 & 2034 & 1920 & 0.9\\
 & tolstoy+23 & FLAMES & 3311 & 1701 & 1522 & 1481 & 0.65\\
 & sestito+23a & GMOS & 2 & 2 & 2 & 2 & 13\\
 & walker+09 & MMFS & 1818 & 1522 & 1417 & 1330 & 1.8\\
 & APOGEE & APOGEE & 5082 & 253 & 102 & 98 & 0.6\\
UMi & combined &  & 4714 & 1225 & 1148 & 831 & 2.3\\
 & sestito+23b & GRACES & 5 & 5 & 5 & 5 & 1.8\\
 & pace+20 & DEIMOS & 1716 & 1538 & 829 & 682 & 2.5\\
 & spencer+18 & Hectoshell & 1407 & 970 & 596 & 406 & 0.9\\
 & APOGEE & APOGEE & 9500 & 279 & 37 & 32 & 0.9\\
\bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_rv_2dhist.pdf}}
\caption[Scl velocity sample]{A plot of the corrected los velocities for
Scl binned in tangent plane coordinates. We detect a slight rotational
gradient towards the bottom right.}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_vel_gradient_binned.pdf}}
\caption[Scl velocity gradient]{A velocity gradient in Sculptor! The
arrow marks the gradient induced by Scl's proper motion on the sky.
\textbf{TODO}: plot of velocity of Scl in direction of gradient.}
\end{figure}

@@

We derive a systemic velocity of \(111.2\pm0.2\) km/s with velocity
dispersion \(9.67\pm0.16\) km/s. Our values are very consistent with
previous work \citep[e.g.][\citet{arroyo-polonio+2024},
\citet{tolstoy+2023}]{WMO2009}.

Finally, we attempt to fit a linear velocity gradient to Scl by adding
parameters for the gradient in \(\xi\) ande \(\eta\). We derive a
gradient of xxx and xxx (see Figure\textasciitilde FIG.), noting that
this direction is different and higher in magnitude than the proper
motion of Scl. Comparing the density difference, we find a bayes factor
of -15. Compared to past work, \citet{battaglia+2008},
\citet{arroyo-polonio+2021}.

Bayes factor found using relative density via KDE with Silverman's
bandwith to prior (XXX theorem).

\emph{Is it interesting that the velocity dispersion of Scl seems to
increase significantly with Rell?}

\begin{table*}[t]
\centering
\caption{MCMC fits for different RV datasets for Scl amoung 3 different models.}
\label{tbl:MCMC-fits-for-different-RV-datasets-for-Scl-amoung-3-different-models}
\begin{tabular}{lllllll}
\toprule
study & mean & sigma & $\partial \log\sigma / \partial \log R$ & $\partial v_z / \partial x$ (km/s/deg) & $\theta_{\rm grad} / ^{\circ}$ & $\log bf$\\
\midrule
all &  &  &  &  &  & \\
 & $111.17\pm0.22$ & $9.68\pm0.17$ & - & - & - & 0\\
 & $111.18 \pm 0.23$ & $9.64\pm0.16$ & - & $4.8\pm1.3$ & $-147_{-12}^{+15}$ & -3.7*\\
 & $111.15\pm0.22$ & $9.70\pm0.16$ & $0.055\pm0.021$ & - & - & -0.8\\
tolstoy+23 &  &  &  &  &  & \\
 & $111.2 \pm 0.3$ & $9.77 \pm 0.18$ & - & - & - & 0\\
 & $111.2\pm0.3$ & $9.73\pm0.18$ & – & $4.8\pm1.4$ & $-154_{-12}^{+16}$ & -2.5\\
 & $111.2 \pm 0.3$ & $9.71\pm0.18$ & $0.081 \pm 0.023$ & – & – & -3.3\\
walker+09 &  &  &  &  &  & \\
 & $111.0\pm0.3$ & $9.57\pm0.21$ & – & – & – & 0\\
 & $111.1\pm0.3$ & $9.54\pm0.21$ & - & $5.3_{-1.6}^{+1.8}$ & $-134_{-16}^{+22}$ & -2.0\\
 & $111.0\pm0.3$ & $9.61\pm0.21$ & $0.03\pm0.03$ & – & – & +1.6\\
apogee &  &  &  &  &  & \\
 & $109.9\pm0.8$ & $8.3\pm0.6$ & – & – & – & –\\
 & $109.9\pm0.8$ & $8.3\pm0.6$ & – & $6\pm3$ & $-151_{-36}^{+44}$ & +0.3\\
 & $109.9\pm0.8$ & $8.3\pm0.7$ & $0.05\pm0.08$ & – & – & +1.1\\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Ursa Minor}\label{ursa-minor}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/umi_rv_2dhist.pdf}}
\caption[UMi velocity sample]{UMi velocities}
\end{figure}

Figure: A plot of the corrected los velocities for UMi binned in tangent
plane coordinates. There is no clear rotation or velocity gradient here.
Interestingly, many velocity members are as far as 100 arcmin away.

For UMi, we collect radial velocities from, APOGEE,
\citet{sestito+2023b}, \citet{pace+2020}, and \citet{spencer+2018}.

We shifted the velocities of \citet{spencer+2018} (\(-1.1\) km/s) and
\citet{pace+2020} (\(+1.1\) km/s) to reach the same scale. We found 183
crossmatched common stars (passing 3\(\sigma\) RV cut, velocity
dispersion cut, and PSAT J+24 \textgreater{} 0.2 w/o velocities). Since
the median difference in velocities in this crossmatch is about 2.2
km/s, we adopt 1 km/s as the approximate systematic error here.

UMi interestingly has a more structured observational pattern, but does
not appear to have any significant velocity substructure.

\begin{table*}[t]
\centering
\caption{MCMC fits for UMi velocity dispersion.}
\label{tbl:MCMC-fits-for-UMi-velocity-dispersion}
\begin{tabular}{lllll}
\toprule
study & mean & sigma & $\log bf_{\rm sigma}$ & $\log bf_{\rm grad}$\\
\midrule
all & $-245.9\pm0.3$ & $8.76\pm0.24$ & +1.5 & +2.2\\
pace & $-244.5\pm0.4$ & $9.1\pm0.3$ & +0.2 & +1.1\\
spencer & $-246.9\pm0.4$ & $8.8\pm0.3$ & +1.8 & -0.3\\
apogee & $-248.2\pm1.6$ & $9.0_{-1.1}^{+1.3}$ & +0.8 & +0.8\\
\bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_umi_fornax_exp_fit.pdf}}
\caption[Classical dwarf density profiles]{The density profiles of
Sculptor, Ursa Minor, and Fornax compared to Exp2D and Plummer density
profiles. Dwarf galaxies are scaled to the same half-light radius and
density at half-light radius (fit from the inner 3 scale radii
exponential recursively. )}\label{fig:classical_dwarfs_densities}
\end{figure}

\section{Appendix / Extra Notes}\label{appendix-extra-notes}

\subsection{Additional density profile
tests}\label{additional-density-profile-tests}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_density_methods_extra.pdf}}
\caption[Density profiles]{Density profiles for various assumptions for
Sculptor. PSAT is our fiducial 2-component J+24 sample, circ is a
2-component bayesian model assuming circular radii, simple is the series
of simple cuts described in Appendix ?, bright is the sample of the
brightest half of stars (scaled by 2), DELVE is a sample of RGB stars
(background subtracted and rescaled to
match).}\label{fig:sculptor_observed_profiles}
\end{figure}

Note that a full rigorous statistical analysis would require a
simulation study of injecting dwarfs into Gaia and assessing the
reliability of various methods of membership and density profiles. This
is beyond the scope of this thesis.

\begin{verbatim}
SELECT TOP 1000
       *
FROM delve_dr2.objects
WHERE 11 < ra
and ra < 19
and -37.7 < dec
and dec < -29.7
\end{verbatim}

>>>>

\begin{itemize}
\tightlist
\item
  Solved astrometry, magnitude, and colour.
\item
  High quality astrometry (\texttt{ruwe\ \textless{}=\ 1.3}).
\item
  3\(\sigma\) consistency of measured parallax with dwarf distance
  (typically near zero; with \citet{lindegren+2021} zero-point
  correction).
\item
  Absolute RA and Dec proper motions less than
  10\(\,{\rm mas\ yr^{-1}}\) (corresponding to tangental velocities of
  \(\gtrsim 500\) km/s at distances larger than 10 kpc.).
\item
  small colour excess factor \(|C*| \leq 3\sigma_{C*}(G)\)
  (\citet{riello+2021}).
\item
  22 \textgreater{} G \textgreater{} 5\(\sigma\) brighter than TRGB
  (dereddened). In practice astrometry cuts limit 21 \textgreater{} G.
\item
  Between -0.5 and 2.5 in Bp - Rp (dereddened).
\end{itemize}

Photometry is dereddened using \citet{schlegel+finkbeiner+davis1998}
extinction maps.

@@

Finally, we need to correct the coordinate frames for the solar motion
and on-sky size of the galaxy. The first step is to subtract out the
solar motion from each radial velocity, corresponding to a typical
gradient of \textasciitilde3 km/s across the field. The next step is to
account for the slight differences in the direction of each radial
velocity. Define the \(\hat z\) direction to point parallel to the
direction from the sun to the centre of the dwarf galaxy. Then if
\(\phi\) is the angular distance between the centre of the galaxy and
the individual star, the corrected radial velocity is then \[
v_z = v_{\rm los, gsr}\cos\phi  - v_{\alpha}\cos\theta \sin\phi - v_\delta \sin\theta\sin\phi
\] where
\(v_{\rm tan, R} = d(\mu_{\alpha*}\cos\theta + \mu_\delta \sin \theta)\)
is the radial component of the proper motion with respect to the centre
of the galaxy.This correction is of the order \(v_{\rm tan}\theta\) so
induces a gradient of about \(1 km/s/degree\) for sculptor
\citep[see][]{walker+mateo+olszewski2008}. The uncertainty is then the
velocity uncertainty plus the distance uncertainties times the PM
uncertainty from above. We then use the \(v_z\) values for the following
modelling, however repeating with uncorrected, heliocentric velocities
does not significantly affect the results .

@@

@@

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_umi_rv_fits.pdf}}
\caption{LOS velocity fit to Scl.}
\end{figure}

\textbf{Figure:} Velocity histogram of Scl and UMi in terms of \(v_z\)
(REF). Orange points are from our crossmatched RV membership sample.

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_rv_scatter.pdf}}
\caption[Scl velocity sample]{RV members of Scl plotted in the tangent
plane coloured by corrected velocity difference from mean
\(v_z - \bar v_z\) . The black ellipse marks the half-light radius in
fig.~\ref{fig:scl_selection}. The black and green arrows mark the proper
motion (PM, GSR frame) and derived velocity gradient (rot) vectors (to
scale).}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_vel_gradient_scatter.pdf}}
\caption[Scl velocity gradient]{The corrected LOS velocity along the
best fit rotational axis. RV members are black points, the systematic
\(v_z\) is the horizontal grey line, blue lines represent the
(projected) gradient from MCMC samples, and the orange line is a rolling
median (with a window size of 50).}
\end{figure}

@@

We additionally add a velocity gradient for Sculptor (adding parameters
A, B \(\sim N(0, 6)\)km/s/deg). We derive a systemic velocity of
\(111.2\pm0.2\) km/s with velocity dispersion \(9.67\pm0.16\) km/s. Our
values are very consistent with previous work
\citep[e.g.][\citet{arroyo-polonio+2024},
\citet{tolstoy+2023}]{WMO2009}. See Appendix for a more detailed
comparison and inter-study tests.

We detect a gradient of \(4.8\pm1.3\) km/s/deg at a position angle of
\(-147_{-12}^{+15}\) degrees. Compared to past work,
\citet{battaglia+2008}, \citet{arroyo-polonio+2024}, our model is XX

For UMi, we collect radial velocities from, APOGEE,
\citet{sestito+2023b}, \citet{pace+2020}, and \citet{spencer+2018}. We
shifted the velocities of \citet{spencer+2018} (\(-1.1\) km/s) and
\citet{pace+2020} (\(+1.1\) km/s) to reach the same scale. We found 183
crossmatched common stars (passing 3\(\sigma\) RV cut, velocity
dispersion cut, and PSAT J+24 \textgreater{} 0.2 w/o velocities). Since
the median difference in velocities in this crossmatch is about 2.2
km/s, we adopt 1 km/s as the approximate systematic error here.

We derive a mean \(-245.9\pm0.3\) and velocity dispersion of
\(8.76\pm0.24\). However, since the velocity means of
\citet{spencer+2018} and \citet{pace+2020} differ by 2 km/s, we add a 1
km/s systematic error to our measurement.

@@

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_umi_fornax_exp_fit.pdf}}
\caption[Classical dwarf density profiles]{The density profiles of
Sculptor, Ursa Minor, and Fornax compared to Exp2D and Plummer density
profiles. Dwarf galaxies are scaled to the same half-light radius and
density at half-light radius (fit from the inner 3 scale radii
exponential recursively. ). Scl and UMi have an excess of stars in the
outer regions (past \(\log R/R_h \sim 0.3\)) compared with
Scl.}\label{fig:classical_dwarfs_densities}
\end{figure}

### 2025-04-25 thesis/introduction.tex
thesis updates and completed test fbest notebook

\begin{table*}[t]
\centering
\caption{Observed properties of Sculptor. References are: 1. Muñoz et al. (2018), 2. Tran et al. (2022), 3. (MV2020b?), 4 McConnachie and Venn (2020).}
\label{tbl:Observed-properties-of-Sculptor-References-are:-1-Muñoz-et-al-2018-2-Tran-et-al-2022-3-MV2020b?-4-McConnachie-and-Venn-2020}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $15.0183 \pm 0.0012^\circ$ & 1\\
$\delta$ & $-33.7186 \pm 0.0007^\circ$ & 1\\
distance modulus & $19.60 \pm 0.05$ (RRL) & 2\\
distance & $83.2 \pm 2$ kpc & 2\\
$\mu_{\alpha*}$ & $0.099 \pm 0.002 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $-0.160 \pm 0.002_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & 3\\
radial velocity & $111.2 \pm 0.2\ {\rm km\,s^{-1}}$ & this work\\
$\sigma_v$ & $9.67\pm0.16\ {\rm km\,s^{-1}}$ & this work\\
$R_h$ & $12.33 \pm 0.05$ arcmin & 4\\
$R_{h,inner}$ & $8.69 \pm 0.2$ arcmin & this work?\\
ellipticity & $0.36 \pm 0.01$ & 1\\
position angle & $92\pm1^\circ$ & 1\\
$M_V$ & $-10.82\pm0.14$ & 1\\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
\centering
\caption{Observed properties of Sculptor. References are: 1. Muñoz et al. (2018), 2. Tran et al. (2022), 3. (MV2020b?), 4 McConnachie and Venn (2020).}
\label{tbl:Observed-properties-of-Sculptor-References-are:-1-Muñoz-et-al-2018-2-Tran-et-al-2022-3-MV2020b?-4-McConnachie-and-Venn-2020}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $15.0183 \pm 0.0012^\circ$ & 1\\
$\delta$ & $-33.7186 \pm 0.0007^\circ$ & 1\\
distance modulus & $19.60 \pm 0.05$ (RRL) & 2\\
distance & $83.2 \pm 2$ kpc & 2\\
$\mu_{\alpha*}$ & $0.099 \pm 0.002 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $-0.160 \pm 0.002_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & 3\\
radial velocity & $111.18 \pm 0.23\ {\rm km\,s^{-1}}$ & this work\\
$\sigma_v$ & $9.71\pm0.17\ {\rm km\,s^{-1}}$ & this work\\
$R_h$ & $12.33 \pm 0.05$ arcmin & 4\\
$R_{h,inner}$ & $8.69 \pm 0.2$ arcmin & this work?\\
ellipticity & $0.36 \pm 0.01$ & 1\\
position angle & $92\pm1^\circ$ & 1\\
$M_V$ & $-10.82\pm0.14$ & 1\\
\bottomrule
\end{tabular}
\end{table*}
